---
title: "NEEPS poster supplemental materials"
pagetitle: "Supplemental materials markdown for my poster at the 2026Northeastern Evolutionary Psychological Society conference"
description-meta: "Lucas Watson is a Ph.D. student at Kansas State University studying dynamic human decision-making from a behavioral and ecological perspective."
title-block-banner: "#cdd99a"
format:
  html:
    quarto-template-params:
      banner-header-class: "sm"
    code-fold: true
    fig-cap-location: bottom
    shift-heading-level-by: 1
resources: 
  - "b4.1.rds"
execute: 
  echo: false
  warning: false
---

## Game

Here is a video playthrough of each level. 

{{<video https://www.youtube.com/embed/PER_TSR3iPc?si=aTIk5BgaFVC6qMd1>}}

Check out how data are tracked in real time.

{{<video data_tracking_lvl_10_video.mp4>}}

## Model

Here is where you can view more detail of the final model I summarized on the poster. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.align = "center", fig.retina = 3,
                      fig.width = 6, fig.height = 6,
                      out.width = "85%", collapse = TRUE,
                      dev = "png", dev.args = list(type = "cairo-png"))

options(digits = 3, width = 120,
        dplyr.summarise.inform = FALSE,
        knitr.kable.NA = "")
```

Model fit with the brms package in R version 4.5.1. Visualization were completed using the ggplot2, tidybayes, bayesplot, and marginaleffects packages. 

```{r}

# load libraries
library(tidyverse)
library(tidybayes)
library(brms)
library(bayesplot)
library(marginaleffects)

# source plot theme
source('project_theme.R')

# load model and data
performance_and_rmi <- read_csv('agg_summary_data.csv')

b4.1 <- read_rds('b4.1.rds')

```

Here is the model summary.

```{r}
print(b4.1)
```

Beta posteriors were shown on the poster, and variance posteriors for each groups' random effect offsets are shown below.

```{r}
as_draws_df(b4.1) |> 
  select(starts_with('sd_')) |> 
  set_names(str_c("sigma[", c('level[intercept]', 'level[rmi]', 'level[time]', 'level[ixn]', 'subject[intercept]', 'subject[rmi]', 'subject[time]', 'subject[ixn]'), "]")) |> 
  pivot_longer(everything()) |> 
  
  # plot
  ggplot(
    aes(x = value, y = fct_reorder(name, value))
  ) +
  stat_halfeye(fill = clrs[2]) +
  scale_y_discrete(labels = ggplot2:::parse_safe) +
  xlim(0, NA) +
  labs(y = 'parameter') +
  project_theme()
```

Here is how model predicted relationships varied by subject.

```{r fig_height = 8}
# now subject spaghetti
predictions(
  b4.1, 
  newdata = datagrid(
    s_rmi = seq(min(performance_and_rmi$s_rmi), max(performance_and_rmi$s_rmi), length.out = 20), 
    s_time_in_game = 0, 
    level = 1:10, 
    subject = unique(performance_and_rmi$subject)
  ), 
  re_formula = NULL, # use everything
  vcov = F
) |> 
  ggplot(aes(x = s_rmi, y = estimate, color = as.factor(subject))) +
  
  # plot spaghetti
  geom_line(
    linewidth = .3, alpha = .4
  ) + 
  
  scale_x_continuous(n.breaks = 10, labels = seq(0, 1, .1)) +
  scale_color_viridis_d(guide = 'none', option = 'magma') +
  
  project_theme() +
  
  labs(x = 'RMI', y = 'Time (s)') +
  
  theme(
    axis.text.x = element_text(size = 8, angle = 90)
  ) +
  
  facet_wrap(~ level)
```

Here is a posterior predictive check to validate the model fit.

```{r fig_height=8}
yrep <- posterior_predict(b4.1, ndraws = 500)

ppc_dens_overlay_grouped(
  performance_and_rmi$true_time, yrep[sample(1:500, 50),], group = performance_and_rmi$level
) + 
  project_theme() + 
  scale_color_manual(values = c(clrs[1], clrs[3])) +
  theme(axis.text = element_text(size = 7)) + 
  labs(
    caption = 'y are the observed data and yrep are the model predicted data for 50 posterior draws'
  )
  
```